dendro

### 2017-04-11 analysis/test-bai.Rmd
update source

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
source(paste0(getwd(),"/script/R/bai_piovesan.R"))
```

# Read data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

## Canar Data

>>>>

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
source('./script/R/bai_piovesan.R')
```

# Read data

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

@@

## San Juan Data
